Combine Files

### 2023-08-09 data/combine_outputs.Rmd
moving things around

geo1 <- import("scopus_combine/geo_country_1.csv")
geo2 <- import("scopus_combine/geo_country_2.csv")

@@

export(geo_together, "py_outputs/geo_country.xlsx", rowNames = F)
```

>>>>

geo1 <- import("data/scopus_combine/geo_country_1.csv")
geo2 <- import("data/scopus_combine/geo_country_2.csv")

@@

export(geo_together, "data/scopus_outputs/geo_country.xlsx", rowNames = F)
```
